### 2016-11-10 datamining/summery.tex
Final notes for exam

\subsubsection{Overfiting and pruning}
There are two strategies to avoid overfiting in tree construction:
Stopping rules, don't expand a node if impurity reduction below some threshold
and pruning, grow a large tree than later merge back nodes.
Stopping rules have a disadvantage that they sometimes require you to make
a weak split to get a good split.
\paragraph{Cost complexity pruning}
A problem with pruning is that the number of pruned subtree is $O(e^n)$.
So cost complexity pruning only considers trees that are
``the best of their kind''.
$T$ denotes the tree with leaf nodes $\overset{\sim}{T}$  and leaf node count
$|\overset{\sim}{T}|$
$R(T)$ denotes the fraction of cases in the training sample that are
misclassified by $T$, the re-substitution error of $T$.
We define the total cost: $C_\alpha(T)=R(T)+\alpha |\overset{\sim}{T}|$
The total cost of tree $T$ consists of the $R(T)$ and a penalty for complexity
$\alpha|\overset{\sim}{T}|$ where $\alpha$ is the parameter that determines the
complexity penalty.
a complex tree that has no errors may have a higher cost than a mall tree with
a number of errors depending on the value of $\alpha (\geq 0)$.
$T_{max}$ denotes the large tree that should be pruned to the right size.
If we fix the value of $\alpha$, therer is a smallest minimizing subtree $T(\alpha)$
of $T_{max}$ that fulfills:
$C_\alpha(T(\alpha))=min T \leq T_{max} C_\alpha(T)$ which says that there is no
subtree of $T_[max]$ with lower cost than $T(\alpha)$, and
If $C_\alpha (T) = C_\alpha(T(\alpha))$ then $T(\alpha) \leq T$ which says that
fi there is a tie then we pick the smallest tree (the one that is a subtree of
all other that achieve the minimum).
It can be shown that for every value of $\alpha$ there is  such a smallest
minimizing subtree. But this is non trivial.
Even though $\alpha$ goes trough a continum of values there is only a finite
numer of sutrees of $T_{max}$. We can construct a descreasing sequence of
subtrees of $T_{max}$: $T_1 > T_2 > ... > {t_1} $ where $t_1$ is the root node,
such tat $T_k$ is the smallest minimizing subtree for
$\alpha \in (\alpha_k, \alpha_{k+1})$. $T_1$ is the smallest subtree of $T_{max}$
with the same resubstitution error as $T_{max}$ ($T_1=T(\alpha=0)$).
the algorithm to find $T_1$ is: find any pair of leaf nodes with a common parent
that can be merged back withoutincreasing te resubtition error. Continue until
no more such pair can be found.
\[g(t)=\frac{R(t)-R(T_{1,t})}{|\overset{\sim}{T}_{1,t}|-1}\]
is a function to calculate the next value for $\alpha$ at which $T_k - T_t$
becomes better than $T_k$.
The algorithm for cost complexity is as follows: We start by computing $T_1$ from $T_{max}$
by using $\alpha = 0$. Then we repeat until we reach the root node:
For each node $t$ in he current tree $T_k$ we compute $g_k(t)$. Then we prune
$T_k$ in all nodes for which $g_k$ achieves the minimum to obtain $T_{k+1}$.
\subsubsection{Selection of the final tree}
$R^{ts}(T)$ denotes the estimated error rate of tree $T$. You can use
the entire set and just pick the one with the lowest estimated error.
There is also cross validation, which can be used if the data set is smaller.

@@

@@

@@

@@

>>>>

It is not correct to only consider splits on the border between
segments in the presence of a minleaf constraint.
\subsubsection{Overfiting and pruning}
There are two strategies to avoid overfiting in tree construction:
Stopping rules, don't expand a node if impurity reduction below some threshold
and pruning, grow a large tree than later merge back nodes.
Stopping rules have a disadvantage that they sometimes require you to make
a weak split to get a good split.
\paragraph{Cost complexity pruning}
A problem with pruning is that the number of pruned subtree is $O(e^n)$.
So cost complexity pruning only considers trees that are
``the best of their kind''.
$T$ denotes the tree with leaf nodes $\overset{\sim}{T}$  and leaf node count
$|\overset{\sim}{T}|$
$R(T)$ denotes the fraction of cases in the training sample that are
misclassified by $T$, the re-substitution error of $T$.
We define the total cost: $C_\alpha(T)=R(T)+\alpha |\overset{\sim}{T}|$
The total cost of tree $T$ consists of the $R(T)$ and a penalty for complexity
$\alpha|\overset{\sim}{T}|$ where $\alpha$ is the parameter that determines the
complexity penalty.
a complex tree that has no errors may have a higher cost than a mall tree with
a number of errors depending on the value of $\alpha (\geq 0)$.
$T_{max}$ denotes the large tree that should be pruned to the right size.
If we fix the value of $\alpha$, therer is a smallest minimizing subtree $T(\alpha)$
of $T_{max}$ that fulfills:
$C_\alpha(T(\alpha))=min T \leq T_{max} C_\alpha(T)$ which says that there is no
subtree of $T_[max]$ with lower cost than $T(\alpha)$, and
If $C_\alpha (T) = C_\alpha(T(\alpha))$ then $T(\alpha) \leq T$ which says that
fi there is a tie then we pick the smallest tree (the one that is a subtree of
all other that achieve the minimum).
It can be shown that for every value of $\alpha$ there is  such a smallest
minimizing subtree. But this is non trivial.
Even though $\alpha$ goes trough a continum of values there is only a finite
numer of sutrees of $T_{max}$. We can construct a descreasing sequence of
subtrees of $T_{max}$: $T_1 > T_2 > ... > {t_1} $ where $t_1$ is the root node,
such tat $T_k$ is the smallest minimizing subtree for
$\alpha \in (\alpha_k, \alpha_{k+1})$. $T_1$ is the smallest subtree of $T_{max}$
with the same resubstitution error as $T_{max}$ ($T_1=T(\alpha=0)$).
the algorithm to find $T_1$ is: find any pair of leaf nodes with a common parent
that can be merged back withoutincreasing te resubtition error. Continue until
no more such pair can be found.
\[g(t)=\frac{R(t)-R(T_{1,t})}{|\overset{\sim}{T}_{1,t}|-1}\]
is a function to calculate the next value for $\alpha$ at which $T_k - T_t$
becomes better than $T_k$.
The algorithm for cost complexity is as follows: We start by computing $T_1$ from $T_{max}$
by using $\alpha = 0$. Then we repeat until we reach the root node:
For each node $t$ in he current tree $T_k$ we compute $g_k(t)$. Then we prune
$T_k$ in all nodes for which $g_k$ achieves the minimum to obtain $T_{k+1}$.
\subsubsection{Selection of the final tree}
$R^{ts}(T)$ denotes the estimated error rate of tree $T$. You can use
the entire set and just pick the one with the lowest estimated error.
There is also cross validation, which can be used if the data set is smaller.

@@

The equation for the cells than is:
$\overset{\wedge}{n}(x)^{\{s+1\}}=\overset{\wedge}{n}(x)^{\{s\}}\frac{n_1(x_1)}{\overset{\wedge}{n}(x)^{\{s\}}}$
where $s$ is the current step in ipf. The margins are replaced for every
iteration by the desired value, whereas the others are calulated, this gives
convergene because you alternate.

@@

\subsection{Chow and lius algorithm}
that maximizes log likelyhood score:
Compute the mutual information between each pair of variables.
Make a complete (undirected) graph where each node corresponds to a variable.
Put the mutual information between a pair of variables as a weight on the edge
between that pair. Compute a maximum weight spanning tree.
Pick a root node, and let all the edges point away from the root.

@@

A-close is more efficient then Apriori on dense, highly correlated data sets.

@@

\section{Social networks}
What progblem do we run into when we want to classify the objects in the test
set of social networks?
To predict the class label of one object,
we need the class labels of the linked objects,
because they determine the value of the link-attributes.
But the class labels of these linked objects are also unknown.
To bootstrap the whole process, we can start with
an initial classification that only uses the node-attributes and disregards the
link- attributes.
Starting from this initial classification we can iteratively improve
the solution.
